---
title: "Forecast NH County Employment"
format: 
    html:
        toc: true
editor: visual
execute: 
  echo: false
  warning: false
  message: false
---

```{r}
# Set up
library(tidyverse)
library(tidyquant)
library(patchwork)

empl_dec_box_fig         <- read_rds("../00_fig/empl_dec_box_fig.rds")
empl_seasonal_north_fig  <- read_rds("../00_fig/empl_seasonal_north_fig.rds")
empl_seasonal_south_fig  <- read_rds("../00_fig/empl_seasonal_south_fig.rds")
empl_seasonal_region_fig <- read_rds("../00_fig/empl_seasonal_region_fig.rds")
corr_with_ma_north_fig   <- read_rds("../00_fig/corr_with_ma_north_fig.rds")
corr_with_ma_south_fig   <- read_rds("../00_fig/corr_with_ma_south_fig.rds")
```

## Overall Trend

* Two States in New Hampshire
* Growing southern counties versus Declining northern counties
* Cheshire in the state's southwestern region resembles northern counties.

```{r fig.height=8}
empl_dec_box_fig + plot_annotation(
    caption = 'Data: U.S. Bureau of Labor Statistics, Employed Persons'
) 
```

# Seasonality

* The seasonal fluctuations in employment in northern counties contrast the stable year-round employment in the southern counties.
* Employment spikes up during the summer months of June, July, and August. This seasonal pattern is particularly noticeable in Belknap and Carroll counties.
* Belknap County also displays many outliers on the lower end. The economy in the Lakes Region outside the peak summer months can struggle far from the norm.
* Interestingly, Merrimack County also displays downside outliers. Unlike Belknap County, however, the outliers are not confined to the non-summer months.

```{r fig.height=7.5}
empl_seasonal_region_fig + 
    
    plot_annotation(caption = 'Data: U.S. Bureau of Labor Statistics, Employed Persons') 
```

```{r}
patchwork <- empl_seasonal_north_fig / empl_seasonal_south_fig

patchwork + 
    
    plot_annotation(caption = 'Data: U.S. Bureau of Labor Statistics, Employed Persons') 
```

# Influence of Massachusetts Economy

* New Hampshire's economy is closely connected with that of Massachusetts. A strong economy in the neighboring state spills over to New Hampshire.
* In particular, the correlation is strong in southernmost counties: Hillsborough, Rockingham, and Strafford. However, Cheshire County does not display correlation as strong.
* Northern counties are not as closely connected to Massachusetts. In particular, Coos County stands out with a strong negative association.

```{r}
patchwork <- corr_with_ma_north_fig / corr_with_ma_south_fig

patchwork + 
    
    plot_annotation(
        title = 'Variations in Cross Correlations in Monthly Employment',
        subtitle = 'between New Hampshire Counties and Massachusetts',
        caption = 'Data: U.S. Bureau of Labor Statistics, Employed Persons'
        )
```
